MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Iterative Model

### 2020-06-10 code/CMC_ExpVal_DataProcessing_deprecated.Rmd
Initial Repo Clean

# Primary variable of interest
postAdjustCovars = c('Institution', 'Reported_Gender', 'Dx' ) #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
#postAdjustCovars = c('Institution', 'Reported_Gender');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'Individual_ID'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
notEstimable = c()

@@

@@

#_#DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,

                    block = COVARIATES1$Individual_ID, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS$E,
            weights = VOOM.WEIGHTS$weights,
            design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
            block = COVARIATES1$Individual_ID, 
            correlation = correlation$cor)

@@

```{r EXP_Val, include=FALSE, eval=TRUE, cache=FALSE}
################################################################################

#CMC ACC DATA
library(stringr)

Associated <- function( Tissue ){
  #'@Tissue either "ACC", or "PFC"

  Correlation <- as.data.frame(Correlation)
  Correlation$Sig <- 'NO'
  Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
  Tab <- table(Correlation$Sig)

  message( paste0(Tissue, ' Mean Correlatioon: ', mean(Correlation$Correlation)) )
  message( paste0(Tissue, ' Mean Std. Dev: ', sd(Correlation$Correlation)) )

@@

  setEPS()
  postscript(paste0( Tissue, "_Cor_gt5Perc.eps"), onefile = TRUE)
    hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  dev.off()
  Filt_Hist <- hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  return(list( TAB=Tab, Correlation=Correlation, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
}

ACC_Plots <- Associated( 'ACC' )
PFC_Plots <- Associated( 'PFC' )
#save.image('Completed_Validation_Analysis.RData')
```

@@

#ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Completed_Validation_Analysis.RData', name = 'RData object of analysis for ACC Validation', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
#  all.annotations$tissueTypeAbrv = 'Analysis'
#  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

>>>>

# Primary variable of interest - , 'Dx'- 
postAdjustCovars = c('Institution', 'Reported_Gender' ) #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
#postAdjustCovars = c('Institution', 'Reported_Gender');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'Individual_ID'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
notEstimable = c()

@@

#InstitutionPitt Reported_GenderMale DxOther DxControl DxSCZ

@@

DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,

                    block = COVARIATES1$Individual_ID, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS$E,
            weights = VOOM.WEIGHTS$weights,
            #_#design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)[ colnames(VOOM.NET.FIT) %in% colnames(VOOM.WEIGHTS$design)] ],
            design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
            block = COVARIATES1$Individual_ID, 
            correlation = correlation$cor)

@@

```{r EXP_Val, include=FALSE, eval=TRUE, cache=FALSE}
################################################################################
#CMC ACC DATA
library(stringr)

Associated <- function( Tissue ){
  #'@Tissue either "ACC", or "PFC"
 Tab
  message( paste0(Tissue, ' Mean Correlatioon: ', mean(Correlation$Correlation)) )
  message( paste0(Tissue, ' Mean Std. Dev: ', sd(Correlation$Correlation)) )

@@

  setEPS()
  postscript(paste0( Tissue, "_Cor_gt5Perc.eps"), onefile = TRUE)
    hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  dev.off()
  Filt_Hist <- hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  return(list( TAB=Tab, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
}

ACC_Plots <- Associated( 'ACC' )
PFC_Plots <- Associated( 'PFC' )

@@
